\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[spanish]{babel}
\usepackage[a4paper,margin=2.5cm]{geometry}
\usepackage[hidelinks]{hyperref}

\title{Bibliografía del artículo \textit{A Unified Approach to Aitchison's, Dually Affine, and Transport Geometries of the Probability Simplex}}
\author{Transcripción de referencia para rastreo bibliográfico}
\date{}

\begin{document}
\maketitle

\noindent Esta lista reproduce la bibliografía del artículo de Pistone y Shoaib
como base de trabajo para ir verificando cada referencia una por una.

\begin{thebibliography}{36}

\bibitem{Amari1987}
Amari, S. \textit{Dual connections on the Hilbert bundles of statistical models}.
In \textit{Geometrization of Statistical Theory}; ULDM Publishing:
Lancaster, PA, USA, 1987; pp. 123--151.

\bibitem{AmariNagaoka2000}
Amari, S.; Nagaoka, H. \textit{Methods of Information Geometry};
Translated from the 1993 Japanese original by Daishi Harada;
American Mathematical Society: Providence, RI, USA, 2000; Volume 191, 206p.

\bibitem{PistoneSempi1995}
Pistone, G.; Sempi, C. An infinite-dimensional geometric structure on the space of all the probability measures equivalent to a given one.
\textit{Ann. Statist.} 1995, \textbf{23}, 1543--1561. [CrossRef]

\bibitem{PawlowskyGlahn2015}
Pawlowsky-Glahn, V.; Egozcue, J.J.; Tolosana-Delgado, R. \textit{Modelling and Analysis of Compositional Data};
John Wiley \& Sons, Ltd.: Hoboken, NJ, USA, 2015. [CrossRef]

\bibitem{Aitchison1986}
Aitchison, J. \textit{The Statistical Analysis of Compositional Data};
Monographs on Statistics and Applied Probability; Chapman \& Hall:
London, UK, 1986; 416p.

\bibitem{Egozcue2012}
Egozcue, J.J.; Pawlowsky-Glahn, V.; Tolosana-Delgado, R.; Ortego, M.I.;
van den Boogaart, K.G. Bayes spaces: Use of improper distributions and
exponential families. \textit{Rev. Real Acad. Cienc. Exactas Fis. Nat. Ser. Mat.}
2012, \textbf{107}, 475--486. [CrossRef]

\bibitem{Barvinok2002}
Barvinok, A. \textit{A Course in Convexity}; Graduate Studies in Mathematics;
American Mathematical Society: Providence, RI, USA, 2002; Volume 54, 366p.

\bibitem{Lay2007}
Lay, S.R. \textit{Convex Sets and Their Applications}; Courier Corporation:
North Chelmsford, MA, USA, 2007.

\bibitem{Amari2016}
Amari, S.I. \textit{Information Geometry and Its Applications}; Applied Mathematical
Sciences; Springer: Tokyo, Japan, 2016; 374p.

\bibitem{NomizuSasaki1994}
Nomizu, K.; Sasaki, T. \textit{Affine Differential Geometry: Geometry of Affine Immersions};
Cambridge Tracts in Mathematics; Cambridge University Press: Cambridge, UK, 1994.

\bibitem{Pistone2020}
Pistone, G. Information Geometry of the Probability Simplex: A Short Course.
\textit{Nonlinear Phenom. Complex Syst.} 2020, \textbf{23}, 221--242. [CrossRef]

\bibitem{ChircoMalagoPistone2022}
Chirco, G.; Malag\`o, L.; Pistone, G. Lagrangian and Hamiltonian dynamics for probabilities
on the statistical bundle. \textit{Int. J. Geom. Methods Mod. Phys.} 2022, \textbf{19}, 2250214.
[CrossRef]

\bibitem{Bourbaki1971}
Bourbaki, N. \textit{Variétés Differentielles et Analytiques. Fascicule de Résultats/Paragraphes 1 à 7};
Springer Science and Business Media: New York, NY, USA, 1971.

\bibitem{Lang1995}
Lang, S. \textit{Differential and Riemannian Manifolds}, 3rd ed.;
Graduate Texts in Mathematics; Springer: New York, NY, USA, 1995; 364p.

\bibitem{Brier1950}
Brier, G.W. Verification of forecasts expressed in terms of probability.
\textit{Mon. Weather. Rev.} 1950, \textbf{78}, 1--3. [CrossRef]

\bibitem{Weyl1952}
Weyl, H. \textit{Space--Time--Matter}; Translation of the 1921 \textit{Raum Zeit Materie};
Dover: New York, NY, USA, 1952.

\bibitem{Brown1986}
Brown, L.D. \textit{Fundamentals of Statistical Exponential Families with Applications in Statistical Decision Theory};
Institute of Mathematical Statistics: Beachwood, OH, USA, 1986; 283p.

\bibitem{EfronHastie2016}
Efron, B.; Hastie, T. \textit{Computer Age Statistical Inference}; IMS Monographs;
Cambridge University Press: Cambridge, UK, 2016; Volume 19, 475p.

\bibitem{CoverThomas2006}
Cover, T.M.; Thomas, J.A. \textit{Elements of Information Theory}, 2nd ed.;
Wiley-Interscience: Hoboken, NJ, USA, 2006; 748p.

\bibitem{OharaAmari1994}
Ohara, A.; Amari, S. Differential geometric structures of stable state feedback systems with dual connections.
\textit{Kybernetika} 1994, \textbf{30}, 369--386.

\bibitem{CafaroAlsing2018}
Cafaro, C.; Alsing, P.M. Decrease of Fisher information and the information geometry of evolution equations
for quantum mechanical probability amplitudes. \textit{Phys. Rev. E} 2018, \textbf{97}, 042110.
[CrossRef] [PubMed]

\bibitem{AyJostLeSchwachhofer2017}
Ay, N.; Jost, J.; L\^e, H.V.; Schwachhöfer, L. \textit{Information Geometry};
Ergebnisse der Mathematik und ihrer Grenzgebiete; Springer: Cham, Switzerland, 2017; 407p.
[CrossRef]

\bibitem{Ohara2017}
Ohara, A. On Affine Immersions of the Probability Simplex and Their Conformal Flattening;
In \textit{Proceedings of the Geometric Science of Information: Third International Conference, GSI 2017},
Paris, France, 7--9 November 2017; Springer: Cham, Switzerland, 2017; pp. 247--254. [CrossRef]

\bibitem{Duy2022}
Duy, T.T.; Nguyen, L.V.; Nguyen, V.; Trung, N.; Abed-Meraim, K. Fisher information neural estimation.
In \textit{Proceedings of the 30th European Signal Processing Conference (EUSIPCO)},
Belgrade, Serbia, 29 August--2 September 2022; pp. 2111--2115. [CrossRef]

\bibitem{Ly2017}
Ly, A.; Marsman, M.; Verhagen, J.; Grasman, R.; Wagenmakers, E. A Tutorial on Fisher Information.
\textit{J. Math. Psychol.} 2017, \textbf{80}, 40--55. [CrossRef]

\bibitem{WeiStocker2016}
Wei, X.X.; Stocker, A. Mutual Information, Fisher Information, and Efficient Coding.
\textit{Neural Comput.} 2016, \textbf{28}, 305--326. [CrossRef] [PubMed]

\bibitem{GibiliscoPistone1998}
Gibilisco, P.; Pistone, G. Connections on non-parametric statistical manifolds by Orlicz space geometry.
\textit{Infin. Dimens. Anal. Quantum Probab. Relat. Top.} 1998, \textbf{1}, 325--347. [CrossRef]

\bibitem{KullbackLeibler1951}
Kullback, S.; Leibler, R.A. On information and sufficiency.
\textit{Ann. Math. Stat.} 1951, \textbf{22}, 79--86. [CrossRef]

\bibitem{Csiszar1975}
Csiszár, I. I-divergence geometry of probability distributions and minimization problems.
\textit{Ann. Probability} 1975, \textbf{3}, 146--158. [CrossRef]

\bibitem{LandauLifshits1980}
Landau, L.D.; Lifshits, E.M. \textit{Statistical Physics}, 3rd ed.; Course of Theoretical Physics;
Butterworth-Heinemann: Oxford, UK, 1980; Volume 5.

\bibitem{PeyreCuturi2019}
Peyré, G.; Cuturi, M. Computational Optimal Transport.
\textit{Found. Trends Mach. Learn.} 2019, \textbf{11}, 355--607. [CrossRef]

\bibitem{Fienberg1980}
Fienberg, S.E. \textit{The Analysis of Cross-Classified Categorical Data};
MIT Press: Cambridge, MA, USA, 1980; 198p.

\bibitem{Arnold1989}
Arnold, V.I. \textit{Mathematical Methods of Classical Mechanics}; Graduate Texts in Mathematics;
Translated from the 1974 Russian original by K. Vogtmann and A. Weinstein;
Springer: New York, NY, USA, 1989; 516p.

\bibitem{Pistone2018}
Pistone, G. Lagrangian Function on the Finite State Space Statistical Bundle.
\textit{Entropy} 2018, \textbf{20}, 139. [CrossRef] [PubMed]

\bibitem{DoCarmo1992}
Do Carmo, M.P. \textit{Riemannian Geometry}; Mathematics: Theory \& Applications;
Translated from the second Portuguese edition by Francis Flaherty;
Birkhäuser Boston Inc.: Basel, Switzerland, 1992; 300p.

\bibitem{ChircoPistone2022}
Chirco, G.; Pistone, G. Dually affine Information Geometry modeled on a Banach space.
\textit{arXiv} 2022, arXiv:2204.00917. [CrossRef]

\end{thebibliography}

\end{document}
